Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-07-18 article.tex
reviewing article for edits

% Packages:

\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}

@@

\section{Introduction}
TODO: refs
The imperative for environmental sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation. This is especially true for Viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries. This study investigates environmental sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs). A broader model of Australian winegrowing was created, with a more specific case study looking at the Coonawarra winegrowing region being conducted to create a rigorous and quantitative approach to understanding sustainable practices and the relationships between these factors.

Bayesian Networks are probabilistic models that effectively capture and analyse the interactions between multiple factors in complex systems. By integrating expert knowledge and region-specific data, BNs were able to provide a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing. This methodology not only shed light on current sustainability practices but also identified critical areas for intervention through illustrating the interconnectedness of each of the factors and how they directly or indirectly influence one another.

This research is guided by several fundamental inquiries aimed at enhancing our understanding of environmental sustainability in viticulture. a primary question is how key factors impacting environmental sustainability can be rigorously defined and quantified. Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how factors influence might change regionally. Additionally, the study investigates how these factors interact within a Bayesian Network model, providing a framework for understanding their complex interdependencies. The final question, looks at how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.

@@

This study provides critical insight into enhancing environmental sustainability through informed decision-making and targeted interventions by highlighting the sensitivity of different factors to the environmental sustainability of vineyards. The findings have significant implications for the local viticulture industry and offer a replicable framework for other agricultural sectors aiming to achieve sustainability.

@@

% end

>>>>

% Packages:
\begin{document}

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{xcolor}

@@

\section{Introduction}

The imperative for environmental sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}. This is especially true for Viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}. This study investigates environmental sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs). A broader model of Australian winegrowing was created, with a more specific case study looking at the Coonawarra winegrowing region being conducted to create a rigorous and quantitative approach to understanding sustainable practices and the relationships between these factors.

Bayesian Networks are probabilistic models that effectively capture and analyse the interactions between multiple factors in complex systems~\cite{korbBayesianArtificialIntelligence2011}. By integrating expert knowledge and region-specific data, BNs were able to provide a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing. This methodology not only shed light on current sustainability practices but also identified critical areas for intervention through illustrating the interconnectedness of each of the factors and how they directly or indirectly influence one another.

This research is guided by several fundamental inquiries aimed at enhancing our understanding of environmental sustainability in viticulture. A primary question is how key factors impacting environmental sustainability can be rigorously defined and quantified. Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how factors influence might change regionally. Additionally, the study investigates how these factors interact within a Bayesian Network model, providing a framework for understanding their complex interdependencies. The final question, looks at how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.

@@

% This study provides critical insight into enhancing environmental sustainability through informed decision-making and targeted interventions by highlighting the sensitivity of different factors to the environmental sustainability of vineyards. The findings have significant implications for the local viticulture industry and offer a replicable framework for other agricultural sectors aiming to achieve sustainability.

@@

\section{References}
% Your references text goes here.
\bibliographystyle{plain}
\bibliography{references}

\end{document}
